A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

\subsection{Simulations}\label{subsection:simulations}
For the simulations, each of the model's domain is initially fully saturated with a fluid (Phase 2), and a wetting phase (1) fluid is driven into the domain from the left hand side at a constant mass flow rate. No flux boundary conditions were imposed on the upper and lower borders of each domain, while mixed fluids are recovered from the right-hand face of the domain. Figure~\ref{fig:PermFields} shows the permeability field for all the cases while Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show phase saturation field during fluid injection for time: $t = 0.15s,~0.30s,~0.50s,~1.15s,~1.75s$ and $2.95s$ for all cases.

>>>>

\subsection{Simulations}\label{subsection:simulations}
For the simulations, each of the model's domain is initially fully saturated with a fluid (Phase 2), and a wetting phase (1) fluid is driven into the domain from the left hand side at a constant mass flow rate. No-flux boundary conditions were imposed on the upper and lower borders of each domain, while mixed fluids are recovered from the right-hand face of the domain. Relative permeability, $\mathcal{K}_{r\alpha}$ (Eqn.~\ref{e:darcy_eqn}), which is often expressed as a function of local, residual and maximum phase saturations prescribed in the pore rock matrix. In the simulations conducted for this work, the modified \citet{Brooks_1964} model was used \citep{alpak_1999},
\begin{eqnarray}
  \mathcal{K}_{rw}\left(S_{w}\right) &=& \mathcal{K}^{\circ}_{rw}\left[\frc{S_{w}-S_{w,irr}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{w}}, \label{Eqn:CoreyBrooks1}\\
  \mathcal{K}_{rnw}\left(S_{nw}\right) &=& \mathcal{K}^{\circ}_{rnw}\left[\frc{S_{nw}-S_{nw,r}}{1-S_{w,irr}-S_{nw,r}}\right]^{n_{nw}}, \label{Eqn:CoreyBrooks2}
\end{eqnarray}
where subscripts $w$ and $nw$ stand for wetting and non-wetting phases, respectively. $\mathcal{K}^{\circ}_{rw}$ and $\mathcal{K}^{\circ}_{rnw}$ are end-point relative permeability to wetting and non-wetting phases, $S_{w,irr}$ and $S_{nw,r}$ are irreducible wetting and residual non-wetting phase saturations, respectively. Exponents $n_{w}$ and $n_{nw}$ are both set to 2.

Figure~\ref{fig:PermFields} shows permeability mapping for all cases, while Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show phase saturation distribution during fluid injection for time,
\begin{displaymath}
  t = 0.15,~0.30,~0.50,~1.15,~1.75\text{ and } 2.95 \text{ s for all cases.} 
\end{displaymath}
